Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
The use of power generation with a renewable energy source is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. 
%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems. We propose a variant of the counterexample guided inductive synthesis approach with two phases linking the technical and cost analysis. First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time. We also compare our formal approach with a commercial simulation tool over real PV systems to show its effectiveness.
%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
\end{abstract}

>>>>

\begin{abstract}
The use of power generation with a renewable energy source is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. 
%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis. 
We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
%First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. 
Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time. We also compare our CEGIS approach with a state-of-the-art commercial tool over real PV systems to show its effectiveness.
%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
\end{abstract}
